TITLE

### 2021-02-18 outputs/paper/paper.Rmd

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(kableExtra)  # for nicer tables

@@

```{r}
survey_1_data <- read_csv(here::here("outputs/survey__data.csv"))
survey_1_data
```

@@

```{r}
survey_2_data <- read_csv(here::here("outputs/survey_2_data.csv"))
survey_2_data
```

@@

Survey 1 data as baseline

Counterfactuals

@@

@@

Suggestions: technical support for restaurants to increase takeout business

@@

Suggestions: grants for minority business owners

@@

External validity, internal validity, cluster sampling. Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.

>>>>

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(kableExtra)  # for nicer tables
library(here) # for working in an RProject

@@

@@

@@

```{r}
survey_1 <- read_csv(here("outputs/data/survey_1.csv"))
survey_2 <- read_csv(here("outputs/data/survey_2.csv"))
```

## Survey 1 results
```{r}
treat1 <- subset(survey_1, group == "treatment")
control1 <- subset(survey_1, group == "control")
t.test(treat1$revenue, control1$revenue)
```

```{r}
survey_1 %>%
  group_by(group) %>%
  summarise(mean_revenue = mean(revenue, na.rm = TRUE),
            median_revenue = median(revenue, na.rm = TRUE),
            n = n())
```

```{r}
survey_1 %>%
  ggplot(aes(x = revenue)) +
  geom_histogram() +
  facet_wrap(~group)
```
Survey 1 data as baseline

Counterfactuals established.

## Survey 2 results

@@

```{r}
survey_2 %>%
  group_by(group) %>%
  summarise(mean_revenue = mean(revenue, na.rm = TRUE),
            median_revenue = median(revenue, na.rm = TRUE),
            n = n())
```

```{r}
treat2 <- subset(survey_2, group == "treatment")
control2 <- subset(survey_2, group == "control")
t.test(treat2$revenue, control2$revenue)
```

```{r}
survey_2 %>%
  ggplot(aes(x = revenue)) +
  geom_histogram() +
  facet_wrap(~group)
```

@@

Suggestion: technical support for restaurants to increase takeout business

@@

Suggestion: grants for minority business owners

@@

External validity, internal validity, cluster sampling. Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them. It was ethically unsound to run the experiment on the entire province, so sampling was necessary.
